AA Distributed Software Development Methodology

### 2013-06-02 front-matter.tex
adicionado Penalva nos autores e 2 bibs
merged hybrid abstract changes

\begin{abstract}
We present a new self-regulating methodology for coordinating
distributed team work called Algorithmic Auto-regulation (AA), based
on recent social networking concepts and individual merit. Team
members take on an egalitarian role, and stay voluntarily logged into
so-called AA sessions for part of their time (e.g.\ 2 hours per day),
during which they create periodical logs --- short text sentences ---
they wish to share about their activity with the team. These logs are
publicly aggregated in a Website and are peer-validated, as in code
review. A video is generally recorded by the members to make their
work logs more understandable. This methodology is well-suited for
increasing the efficiency of distributed teams working on what is
called Global Software Development (GSD) through asynchronous
on-demand communication, reducing the need for central management,
unproductive meetings or time-consuming reports. The AA methodology
also legitimizes the activities of a distributed software team.  It
thus enables entities to have a solid means to fund these activities,
allowing for new and concrete business models to emerge for very
distributed software development. AA as a methodology is also at the
core of having self-replicating hacker initiatives. These claims are
discussed in a real case-study of running a distributed free software
hacker team called Lab Macambira.
\end{abstract}

>>>>

\begin{abstract}
We present a new self-regulating methodology for coordinating distributed team
work called Algorithmic Auto-regulation (AA), based on recent social networking
concepts and individual merit. Team members take on an egalitarian role, and
stay voluntarily logged into so-called AA sessions for part of their time (e.g.\
2 hours per day), during which they create periodical logs --- short text
sentences --- they wish to share about their activity with the team. These logs
are publicly aggregated in a Website and are peer-validated after the end of a
session, as in code review.  A short screencast is ideally recorded at the end
of each session to make AA logs more understandable.  This methodology has shown
to be well-suited for increasing the efficiency of distributed teams working on
what is called Global Software Development (GSD), as observed in our experience
in actual real-world situations.  This efficiency boost is mainly achieved through 1)
built-in asyncrhonous on-demand communication, documentation of work products
and processes, and 2) reduced need for central management, meetings or
time-consuming reports. Hence, the AA methodology legitimizes and facilitates
the activities of a distributed software team.  It thus enables other entities
to have a solid means to fund these activities, allowing for new and concrete
business models to emerge for very distributed software development. AA has been
proposed, at its core, as a way of sustaining self-replicating hacker
initiatives. These claims are discussed in a real case-study of running a
distributed free software hacker team called Lab Macambira.  
\end{abstract}
